Multi-level generalizations of collective spin dynamics and squeezing

### 2019-10-10 collective_sun/sun_notes.tex
changed sign conventions in the definition of the transition operator new sign convention is consistent with existing literature
changed sign conventions in SOC phase

The GGM operators in \eqref{eq:GGM_diag} and \eqref{eq:GGM_off_diag}
provide a convenient operator basis to describe dynamics obeying
SU($n$) symmetry.  An external driving field addressing $n$-level
nuclear spins, however, will generally violate SU($n$) symmetry, and
instead obeys the symmetries of the {\it polarization} or {\it
  transition operators} defined by\cite{kryszewski2006alternative,
  bertlmann2008bloch}
\begin{align}
  T_{LM}
  \equiv \p{-1}^M \sqrt{\f{2L+1}{2I+1}} \sum_{\mu,\nu}
  \bk{I\mu;LM|I\nu} \op{\nu}{\mu},
  \label{eq:trans_ops}
\end{align}
where $L\in\set{0,1,\cdots,n-1}$ and $M\in\set{-L,-L+1,L}$ index a
total spin and its projection onto a quantization axis;
$I\equiv\p{n-1}/2$ is the maximal angular momentum of an $n$-level
spin; $\mu,\nu\in\set{-I,-I+1,\cdots,I}$ index projections of an
$n$-level nuclear spin onto a quantization axis; and
$\bk{I\mu;LM|I\nu}$ is a Clebsch-Gordan coefficient.  Note that our
definition of a transition operators differs from that in
Refs.~\cite{kryszewski2006alternative, bertlmann2008bloch} by the sign
$\p{-1}^M$; this choice of sign convention will simplify much of our
work below.

The transition operator $T_{LM}$ is proportional to the transition
induced on a nuclear spin by the absorption of a spin-$L$ particle
with spin projection $M$ onto a quantization axis.  Similarly to the
GGM operators in \eqref{eq:GGM_diag} and \eqref{eq:GGM_off_diag}, the
transition operators in \eqref{eq:trans_ops} provide a complete basis
for the space of operators on the Hilbert space of an $n$-level
system, and satisfy the orthonormality condition
\begin{align}
  \obk{T_{LM}|T_{L'M'}} = \delta_{LL'} \delta_{MM'},
\end{align}
which implies
\begin{align}
  H_{\t{int}} = -\f{u}{2} \sum_{p,q} {\v T^{(p)}}^\dag \c \v T^{(q)}
  = -\f{u}{2} \v\T^\dag \c \v\T,
  &&
  \v\T \equiv \sum_p\v T^{(p)},
  \label{eq:H_int_trans}
\end{align}
where $\v T$ is a vector of all transition operators in
\eqref{eq:trans_ops}.

@@

Unlike the GGM operators in \eqref{eq:GGM_diag} and
\eqref{eq:GGM_off_diag}, the transition operators in
\eqref{eq:trans_ops} are not self-adjoint.  In order to express
Hamiltonians in terms of self-adjoint operators, we define the {\it
  drive operators}
\begin{align}
  D_{L,0} \equiv T_{L,0},
  &&
  D_{LM} \stackrel{M\ne0}{\equiv} \f{\sigma_M}{\sqrt{2}}
  \sp{T_{L\abs{M}} + \sign\p{M}T_{L\abs{M}}^\dag},
  &&
  \sigma_M \equiv \sign\p{M}^{3/2},
  \label{eq:drive_ops}
\end{align}
for integer $M$ with $\abs{M}\le L$.  The drive operator $D_{LM}$ is
proportional to the Hamiltonian induced on a nuclear spin by an
external classical field of spin-$L$ particles with spin projection
$M$ onto a quantization axis.  Similarly to the GGM operators in
\eqref{eq:GGM_diag} and \eqref{eq:GGM_off_diag}, the drive operators
are proportional to the Pauli operators in the case of $n=2$, and
satisfy the orthonormality condition
\begin{align}
  \obk{D_{LM}|D_{L'M'}} = \delta_{LL'}\delta_{MM'},
\end{align}
which implies
\begin{align}
  H_{\t{int}} = -\f{u}{2} \sum_{p,q} \v D^{(p)}\c\v D^{(q)}
  = -\f{u}{2} \v\D \c \v\D,
  &&
  \v\D \equiv \sum_p \v D^{(p)},
  \label{eq:H_int_drive}
\end{align}
where $\v D$ is a vector of all drive operators in
\eqref{eq:drive_ops}.

@@

An driving laser addressing spin-$1/2$ fermions on a 1-D lattice will
induce the Hamiltonian
\begin{align}
  \left. H_{\t{drive}}^{(\phi)} \right|_{n=2}
  = \Omega \sum_j
  \p{e^{-i\phi j} c_{j,\up}^\dag c_{j,\dn}
    + e^{i\phi j} c_{j,\dn}^\dag c_{j,\up}},
  \label{eq:H_drive_2}
\end{align}
where $\Omega$ is a (real) driving amplitude, $j\in\mathbb{Z}$ indexes
a lattice site, and $\phi$ is the relative phase of the drive between
adjacent lattice sites.  The multi-level analogue of
\eqref{eq:H_drive_2} is
\begin{align}
  H_{\t{drive}}^{(\phi)}
  = -\Omega \sum_j \p{e^{-i\phi j} T_{1,1}^{(j)}
    + e^{i\phi j} {T_{1,1}^{(j)}}^\dag}
  = \Omega \D_{1,1}^{(\phi)},
  \label{eq:H_drive}
\end{align}
where
\begin{align}
  \D_{LM}^{(\phi)}
  \equiv \sum_j \sp{\cos\p{M\phi j} D_{LM}^{(j)}
    + \sin\p{M\phi j} D_{L,-M}^{(j)}},
  \label{eq:drive_rot}
\end{align}
is an inhomogeneously rotated collective drive operator.  We can make
this drive spatially homogenous via the gauge transformation
$c_{j\mu}^\dag \to e^{i\mu\phi j} c_{j\mu}^\dag$, which takes
\begin{align}
  H_{\t{drive}}^{(\phi)} \to H_{\t{drive}} = \Omega \D_{1,1}.
\end{align}
The SU($n$) symmetry of collective interactions implies that the
interaction Hamiltonian $H_{\t{int}}$ in \eqref{eq:H_int_drive} is
invariant under this gauge transformation, but the single-particle
Hamiltonian in \eqref{eq:H_lat} transforms as (see Appendix
\ref{sec:lat_drive})
\begin{align}
  H_{\t{lat}}
  \to H_{\t{lat}}^{(\phi)}
  = -J \sum_{q,\mu} \cos\p{qa-\mu\phi} c_{q\mu}^\dag c_{q\mu}
  = \sum_{q,L} B_L^{(\phi,q)} D_{L,0}^{(q)},
  \label{eq:H_lat_SOC}
\end{align}
with effective inhomogeneous driving field amplitudes
\begin{align}
  B_L^{(\phi,q)} = -J w_L\p{qa} A_L^{(\phi)},
\end{align}
where
\begin{align}
  w_L\p{\theta} \equiv
  \begin{cases}
    \cos\theta & L~\t{even} \\
    \sin\theta & L~\t{odd}
  \end{cases},
  &&
  A_L^{(\phi)} \equiv \sqrt{\f{2L+1}{n}}
  \sum_\mu \bk{I\mu;L,0|I\mu} w_L\p{\mu\phi}.
\end{align}
Spin-orbit coupling with multi-level systems thus allows for the
simulation of synthetic gauge fields with large spin ($L>1$).  As we
will see in the following section, multi-laser drives can also
simulate synthetic large-spin fields with non-zero spin projection
($M\ne0$) onto a quantization axis.

In the regime of weak SOC with $\abs{\phi}\ll1$, by considering
\begin{enumerate*}
\item all $L\le12$ for arbitrary $n$, and
\item all $L<n$ for all $n\le25$
\end{enumerate*}
(and conjecturing the same pattern for all $L$ and $n$), we find that
% expand Clebsch-Gordan coefficients in a power series according to
% \url{functions.wolfram.com/07.38.06.0008.01}
\begin{align}
  A_L^{(\phi)} = c_L \sqrt{n_L}\, \phi^L + O\p{\phi^{L+2}},
  \label{eq:A_L_phi_small}
\end{align}
where
\begin{align}
  c_L \equiv \p{-1}^{\lfloor L/2\rfloor}
  \sqrt{2L+1}\, \f{L!}{\p{2L+1}!},
  &&
  n_L \equiv \prod_{\ell=-L}^L\p{n-\ell}.
\end{align}

@@

  = \sum_j \sum_{m\in\set{1,0,-1}} \p{\Omega_m e^{-i\phi_m j}

@@

  \f{\Omega_0\Omega_s}{\Delta} e^{-i\p{\phi_s-\phi_0} j}

@@

  \f{\Omega_+\Omega_-}{\Delta} e^{-i\p{\phi_s-\phi_{-s}}j}

@@

$\mu\to\mu+m$ on site $j$ imprints the phase $-m\phi j$, then the
drive $H_{\t{Raman}}^{(\phi)}$ takes the form

@@

Here we derive the drive-operator ($D_{LM}$) expansion of the
spin-orbit coupled Hamiltonian $H_{\t{lat}}^{(\phi)}$ in
\eqref{eq:H_lat_SOC}.  In the basis of spin operators
$s_{\mu\mu}^{(q)} \equiv c_{q\mu}^\dag c_{q\mu}$, this Hamiltonian
takes the form
\begin{align}
  H_{\t{lat}}^{(\phi)}
  = -J \sum_{q,\mu} \cos\p{qa-\mu\phi} s_{\mu\mu}^{(q)}
  \label{eq:H_lat_spin}
\end{align}
Defining the diagonal ``spin-wave'' operators
\begin{align}
  \tilde d_{\phi+} \equiv \sum_\mu \cos\p{\mu\phi} s_{\mu\mu},
  &&
  \tilde d_{\phi-} \equiv \sum_\mu \sin\p{\mu\phi} s_{\mu\mu},
\end{align}
which are respectively even and odd under spin inversion
($\mu\to-\mu$), we can expand
\begin{align}
  \sum_\mu \cos\p{qa+\mu\phi} s_{\mu\mu}
  = \cos\p{qa} \tilde d_{\phi+} + \sin\p{qa} \tilde d_{\phi-},
\end{align}
and resolve the identity (super-)operator $\I$ with
$\I \tilde d_{\phi\pm} = \tilde d_{\phi\pm}$ in the basis of the drive operators
$D_{LM}$ (see Appendix \ref{sec:changing_bases}), finding
\begin{align}
  \sum_\mu \cos\p{qa+\mu\phi} s_{\mu\mu}
  = \cos\p{qa} \f12 \sum_{L,M} \obk{\tilde d_{\phi+}|D_{LM}} D_{LM}
  + \sin\p{qa} \f12 \sum_{L,M} \obk{\tilde d_{\phi-}|D_{LM}} D_{LM}.
\end{align}
We now note that the drive operators $D_{LM}$ are strictly
off-diagonal for $M\ne0$, and furthermore that $D_{L,0}$ with even
(odd) $L$ is even (odd) under spin inversion, which implies
\begin{align}
  \sum_{L,M} \obk{\tilde d_{\phi+}|D_{LM}} D_{LM}
  = \sum_{L\,\t{even}} \obk{\tilde d_{\phi+}|D_{L,0}} D_{L,0},
\end{align}
and likewise with $\tilde d_{\phi-}$ and odd $L$.  In total, we can
write
\begin{align}
  \sum_\mu \cos\p{qa+\mu\phi} s_{\mu\mu}
  = \cos\p{qa} \f12 \sum_{L\,\t{even}}
  \obk{\tilde d_{\phi+}|D_{L,0}} D_{L,0}
  + \sin\p{qa} \f12 \sum_{L\,\t{odd}}
  \obk{\tilde d_{\phi-}|D_{L,0}} D_{L,0},
\end{align}
or, more compactly,
\begin{align}
  \sum_\mu \cos\p{qa+\mu\phi} s_{\mu\mu}
  = \sum_L w_L\p{qa} A_L^{(\phi)} D_{L,0},
  &&
  w_L\p{\theta} \equiv
  \begin{cases}
    \cos\theta & L~\t{even} \\
    \sin\theta & L~\t{odd}
  \end{cases},
  \label{eq:compact_SOC_drive}
\end{align}
with effective driving field amplitudes
\begin{align}
  A_L^{(\phi)}
  \equiv \f12 \obk{\tilde d_{\phi,\p{-1}^L}|D_{L,0}}
  = \f12 \sum_\mu w_L\p{\mu\phi} \obk{s_{\mu\mu}|D_{L,0}}
  = \sqrt{\f{2L+1}{n}}
  \sum_\mu \bk{I\mu;L,0|I\mu} w_L\p{\mu\phi}.
\end{align}
Substituting the result in \eqref{eq:compact_SOC_drive} into the
single-particle Hamiltonian in \eqref{eq:H_lat_spin} yields
\begin{align}
  H_{\t{lat}}^{(\phi)} = \sum_{q,L} B_L^{(\phi,q)} D_{L,0}^{(q)},
  &&
  B_L^{(\phi,q)} \equiv -J w_L\p{qa} A_L^{(\phi)}.
\end{align}

@@

The drive operators are defined by
\begin{align}
  D_{L,0} \equiv T_{L,0},
  &&
  D_{LM} \stackrel{M\ne0}{\equiv} \f{\sigma_M}{\sqrt{2}}
  \sp{T_{L\abs{M}} + \sign\p{M}T_{L\abs{M}}^\dag},
  &&
  \sigma_M \equiv \sign\p{M}^{3/2},
\end{align}
and can alternately be expressed as
\begin{align}
  D_{LM} = \f{\tau_M}{\sqrt{2}} \p{T_{LM} + \epsilon_M T_{L,-M}},
\end{align}
where
\begin{align}
  \tau_M \equiv
  \begin{cases}
    \sqrt{2} & M = 0, \\
    \sign\p{M}^{M+1/2} & M \ne 0
  \end{cases},
  &&
  \epsilon_M \equiv \p{-1}^M \sign\p{M},
\end{align}
which also implies that
\begin{align}
  T_{LM} = \f{\tilde\tau_M}{\sqrt{2}} \p{D_{LM} + i D_{L,-M}},
  &&
  \tilde\tau_M \equiv
  \begin{cases}
    \sqrt{2}/\p{1+i} & M = 0 \\
    \sign\p{M}^{M-1/2} & M \ne 0
  \end{cases}.
\end{align}
In order to evaluate the product of two drive operators, we can thus
expand them in terms of transition operators, evaluate the
corresponding products of transition operators (see Appendix
\ref{sec:trans_prod}), and finally expand the result in terms of drive
operators.  The general product of two drive operators takes the form
\begin{align}
  D_{\ell_1 m_1} D_{\ell_2 m_2}
  = \f{\tau_{m_1}\tau_{m_2}}{\sqrt{2}}
  \sum_L \p{f_{\ell_1 m_1;\ell_2 m_2}^{L,m_1+m_2}
    E_{\ell_1 m_1;\ell_2 m_2}^{(L,+)}
    + f_{\ell_1 m_1;\ell_2,-m_2}^{L,m_1-m_2}
    E_{\ell_1 m_1;\ell_2 m_2}^{(L,-)}},
\end{align}
with operators
\begin{align}
  E_{\ell_1 m_1;\ell_2 m_2}^{(L,+)}
  &\equiv \sum_{s\in\set{\pm1}}
  \f12 \sp{\tilde\tau_{m_1+m_2}
    + i s \p{-1}^{L+\ell_1+\ell_2}
    \epsilon_{m_1} \epsilon_{m_2} \tilde\tau_{-\p{m_1+m_2}}}
  \sqrt{s} D_{L,s\p{m_1+m_2}},
  \\
  E_{\ell_1 m_1;\ell_2 m_2}^{(L,-)}
  &\equiv \sum_{s\in\set{\pm1}}
  \f12 \sp{\epsilon_{m_2} \tilde\tau_{m_1-m_2}
    + i s \p{-1}^{L+\ell_1+\ell_2}
    \epsilon_{m_1} \tilde\tau_{-\p{m_1-m_2}}}
  \sqrt{s} D_{L,s\p{m_1-m_2}}.
\end{align}
If $m_1\pm m_2=0$, these operators simplify to
\begin{align}
  E_{\ell_1 m;\ell_2,-m}^{(L,+)}
  &= \f1{\sqrt{2}} \sp{1 - \p{-1}^{L+\ell_1+\ell_2}
    \p{1-\delta_{m,0}}} D_{L,0}, \\
  E_{\ell_1 m;\ell_2 m}^{(L,-)}
  &= \f{\epsilon_m}{\sqrt{2}}
  \sp{1 + \p{-1}^{L+\ell_1+\ell_2}} D_{L,0},
\end{align}
and are otherwise
\begin{align}
  E_{\ell_1 m_1;\ell_2 m_2}^{(L,+)}
  &\stackrel{m_1+m_2\ne0}{=}
  \tau_{m_1+m_2}^* \sum_{s\in\set{\pm1}}
  \f12 \sp{1 + s \p{-1}^{L+\ell_1+\ell_2}
    \epsilon_{m_1} \epsilon_{m_2} \epsilon_{m_1+m_2}}
  \sqrt{s} D_{L,s\p{m_1+m_2}}, \\
  E_{\ell_1 m_1;\ell_2 m_2}^{(L,-)}
  &\stackrel{m_1-m_2\ne0}{=}
  \tau_{m_1-m_2}^* \sum_{s\in\set{\pm1}}
  \f12 \sp{\epsilon_{m_2} + s \p{-1}^{L+\ell_1+\ell_2}
    \epsilon_{m_1} \epsilon_{m_1-m_2}}
  \sqrt{s} D_{L,s\p{m_1-m_2}}.
\end{align}
If $\p{m_1,m_2}=\p{0,m}$, then we can use the fact that
$i\tau_m\tau_{-m}^*=\epsilon_m$ for $m\ne0$ to simplify
\begin{align}
  D_{\ell_1,0} D_{\ell_2 m}
  = \sum_L f_{\ell_1,0,\ell_2,m}^{Lm}
  \sum_{s\in\set{\pm1}} \f12 \sp{1 + s \p{-1}^{L+\ell_1+\ell_2}}
  \sqrt{s} D_{L,sm}.
\end{align}

>>>>

The GGM operators in \eqref{eq:GGM_diag} and \eqref{eq:GGM_off_diag}
provide a convenient operator basis to describe dynamics obeying
SU($n$) symmetry.  An external driving field addressing $n$-level
nuclear spins, however, will generally violate SU($n$) symmetry, and
instead obeys the symmetries of the {\it polarization} or {\it
  transition operators} defined by\cite{kryszewski2006alternative,
  bertlmann2008bloch}
\begin{align}
  T_{LM}
  \equiv \sqrt{\f{2L+1}{2I+1}} \sum_{\mu,\nu}
  \bk{I\mu;LM|I\nu} \op{\nu}{\mu},
  \label{eq:trans_ops}
\end{align}
where $L\in\set{0,1,\cdots,n-1}$ and $M\in\set{-L,-L+1,L}$ index a
total spin and its projection onto a quantization axis;
$I\equiv\p{n-1}/2$ is the maximal angular momentum of an $n$-level
spin; $\mu,\nu\in\set{-I,-I+1,\cdots,I}$ index projections of an
$n$-level nuclear spin onto a quantization axis; and
$\bk{I\mu;LM|I\nu}$ is a Clebsch-Gordan coefficient.  The transition
operator $T_{LM}$ is proportional to the transition induced on a
nuclear spin by the absorption of a spin-$L$ particle with spin
projection $M$ onto a quantization axis.  Similarly to the GGM
operators in \eqref{eq:GGM_diag} and \eqref{eq:GGM_off_diag}, the
transition operators in \eqref{eq:trans_ops} provide a complete basis
for the space of operators on the Hilbert space of an $n$-level
system, and satisfy the orthonormality condition
\begin{align}
  \obk{T_{LM}|T_{L'M'}} = \delta_{LL'} \delta_{MM'},
\end{align}
which implies
\begin{align}
  H_{\t{int}} = -\f{u}{2} \sum_{p,q} {\v T^{(p)}}^\dag \c \v T^{(q)}
  = -\f{u}{2} \v\T^\dag \c \v\T,
  &&
  \v\T \equiv \sum_p\v T^{(p)},
  \label{eq:H_int_trans}
\end{align}
where $\v T$ is a vector of all transition operators in
\eqref{eq:trans_ops}.

@@

Unlike the GGM operators in \eqref{eq:GGM_diag} and
\eqref{eq:GGM_off_diag}, the transition operators in
\eqref{eq:trans_ops} are not self-adjoint.  In order to express
Hamiltonians in terms of self-adjoint operators, we define the {\it
  drive operators}
\begin{align}
  D_{L,0} \equiv T_{L,0},
  &&
  D_{LM} \stackrel{M\ne0}{\equiv} \f{\sigma_M}{\sqrt{2}}
  \sp{T_{L\abs{M}} + \sign\p{M}T_{L\abs{M}}^\dag},
  &&
  \sigma_M \equiv \p{-1}^M \sign\p{M}^{3/2},
  \label{eq:drive_ops}
\end{align}
for integer $M$ with $\abs{M}\le L$.  The drive operator $D_{LM}$ is
proportional to the Hamiltonian induced on a nuclear spin by an
external classical field of spin-$L$ particles with spin projection
$M$ onto a quantization axis.  Similarly to the GGM operators in
\eqref{eq:GGM_diag} and \eqref{eq:GGM_off_diag}, the drive operators
are proportional to the Pauli operators in the case of $n=2$, and
satisfy the orthonormality condition
\begin{align}
  \obk{D_{LM}|D_{L'M'}} = \delta_{LL'}\delta_{MM'},
\end{align}
which implies
\begin{align}
  H_{\t{int}} = -\f{u}{2} \sum_{p,q} \v D^{(p)}\c\v D^{(q)}
  = -\f{u}{2} \v\D \c \v\D,
  &&
  \v\D \equiv \sum_p \v D^{(p)},
  \label{eq:H_int_drive}
\end{align}
where $\v D$ is a vector of all drive operators in
\eqref{eq:drive_ops}.

@@

A driving laser addressing spin-$1/2$ fermions on a 1-D lattice will
induce the Hamiltonian
\begin{align}
  \left. H_{\t{drive}}^{(\phi)} \right|_{n=2}
  = \Omega \sum_j
  \p{e^{i\phi j} c_{j,\up}^\dag c_{j,\dn}
    + e^{-i\phi j} c_{j,\dn}^\dag c_{j,\up}},
  \label{eq:H_drive_2}
\end{align}
where $\Omega$ is a (real) driving amplitude, $j\in\mathbb{Z}$ indexes
a lattice site, and $\phi$ is the relative phase of the drive between
adjacent lattice sites.  The multi-level analogue of
\eqref{eq:H_drive_2} is
\begin{align}
  H_{\t{drive}}^{(\phi)}
  = -\Omega \sum_j \p{e^{i\phi j} T_{1,1}^{(j)}
    + e^{-i\phi j} {T_{1,1}^{(j)}}^\dag}
  = \Omega \D_{1,1}^{(\phi)},
  \label{eq:H_drive}
\end{align}
where
\begin{align}
  \D_{LM}^{(\phi)}
  \equiv \sum_j \sp{\cos\p{M\phi j} D_{LM}^{(j)}
    - \sin\p{M\phi j} D_{L,-M}^{(j)}},
  \label{eq:drive_rot}
\end{align}
is an inhomogeneously rotated collective drive operator.  We can make
this drive spatially homogenous via the gauge transformation
$c_{j\mu}^\dag \to e^{-i\mu\phi j} c_{j\mu}^\dag$, which takes
\begin{align}
  H_{\t{drive}}^{(\phi)} \to H_{\t{drive}} = \Omega \D_{1,1}.
\end{align}
The SU($n$) symmetry of collective interactions implies that the
interaction Hamiltonian $H_{\t{int}}$ in \eqref{eq:H_int_drive} is
invariant under this gauge transformation, but the single-particle
Hamiltonian in \eqref{eq:H_lat} transforms as (see Appendix
\ref{sec:lat_drive})
\begin{align}
  H_{\t{lat}}
  \to H_{\t{lat}}^{(\phi)}
  = -J \sum_{q,\mu} \cos\p{qa+\mu\phi} c_{q\mu}^\dag c_{q\mu}
  = \sum_{q,L} B_L^{(\phi,q)} D_{L,0}^{(q)},
  \label{eq:H_lat_SOC}
\end{align}
with effective inhomogeneous driving field amplitudes
\begin{align}
  B_L^{(\phi,q)} = -J w_L\p{qa} A_L^{(\phi)},
\end{align}
where
\begin{align}
  w_L\p{\theta} \equiv
  \begin{cases}
    \cos\theta & L~\t{even} \\
    \sin\theta & L~\t{odd}
  \end{cases},
  &&
  A_L^{(\phi)} \equiv \sqrt{\f{2L+1}{n}}
  \sum_\mu \bk{I\mu;L,0|I\mu} w_L\p{\mu\phi}.
\end{align}
Spin-orbit coupling with multi-level systems thus allows for the
simulation of synthetic gauge fields with large spin ($L>1$).  As we
will see in the following section, multi-laser drives can also
simulate synthetic large-spin fields with non-zero spin projection
($M\ne0$) onto a quantization axis.

In the regime of weak SOC with $\abs{\phi}\ll1$, by considering
\begin{enumerate*}
\item all $L\le12$ for arbitrary $n$, and
\item all $L<n$ for all $n\le25$
\end{enumerate*}
(and conjecturing the same pattern for all $L$ and $n$), we find that
% expand Clebsch-Gordan coefficients in a power series according to
% \url{functions.wolfram.com/07.38.06.0008.01}
\begin{align}
  A_L^{(\phi)} = c_L \sqrt{n_L}\, \phi^L + O\p{\phi^{L+2}},
  \label{eq:A_L_phi_small}
\end{align}
where
\begin{align}
  c_L \equiv \p{-1}^{L+\lfloor L/2\rfloor}
  \sqrt{2L+1}\, \f{L!}{\p{2L+1}!},
  &&
  n_L \equiv \prod_{\ell=-L}^L\p{n-\ell}.
\end{align}

@@

  = \sum_j \sum_{m\in\set{1,0,-1}} \p{\Omega_m e^{i\phi_m j}

@@

  \f{\Omega_0\Omega_s}{\Delta} e^{i\p{\phi_s-\phi_0} j}

@@

  \f{\Omega_+\Omega_-}{\Delta} e^{i\p{\phi_s-\phi_{-s}}j}

@@

$\mu\to\mu+m$ on site $j$ imprints the phase $m\phi j$, then the drive
$H_{\t{Raman}}^{(\phi)}$ takes the form

@@

Here we derive the drive-operator ($D_{LM}$) expansion of the
spin-orbit coupled Hamiltonian $H_{\t{lat}}^{(\phi)}$ in
\eqref{eq:H_lat_SOC}.  In the basis of spin operators
$s_{\mu\mu}^{(q)} \equiv c_{q\mu}^\dag c_{q\mu}$, this Hamiltonian
takes the form
\begin{align}
  H_{\t{lat}}^{(\phi)}
  = -J \sum_{q,\mu} \cos\p{qa+\mu\phi} s_{\mu\mu}^{(q)}
  \label{eq:H_lat_spin}
\end{align}
Defining the diagonal ``spin-wave'' operators
\begin{align}
  \tilde d_{\phi+} \equiv \sum_\mu \cos\p{\mu\phi} s_{\mu\mu},
  &&
  \tilde d_{\phi-} \equiv \sum_\mu \sin\p{\mu\phi} s_{\mu\mu},
\end{align}
which are respectively even and odd under spin inversion
($\mu\to-\mu$), we can expand
\begin{align}
  \sum_\mu \cos\p{qa+\mu\phi} s_{\mu\mu}
  = \cos\p{qa} \tilde d_{\phi+} - \sin\p{qa} \tilde d_{\phi-},
\end{align}
and resolve the identity (super-)operator $\I$ with
$\I \tilde d_{\phi\pm} = \tilde d_{\phi\pm}$ in the basis of the drive operators
$D_{LM}$ (see Appendix \ref{sec:changing_bases}), finding
\begin{align}
  \sum_\mu \cos\p{qa+\mu\phi} s_{\mu\mu}
  = \cos\p{qa} \f12 \sum_{L,M} \obk{\tilde d_{\phi+}|D_{LM}} D_{LM}
  - \sin\p{qa} \f12 \sum_{L,M} \obk{\tilde d_{\phi-}|D_{LM}} D_{LM}.
\end{align}
We now note that the drive operators $D_{LM}$ are strictly
off-diagonal for $M\ne0$, and furthermore that $D_{L,0}$ with even
(odd) $L$ is even (odd) under spin inversion, which implies
\begin{align}
  \sum_{L,M} \obk{\tilde d_{\phi+}|D_{LM}} D_{LM}
  = \sum_{L\,\t{even}} \obk{\tilde d_{\phi+}|D_{L,0}} D_{L,0},
\end{align}
and likewise with $\tilde d_{\phi-}$ and odd $L$.  In total, we can
write
\begin{align}
  \sum_\mu \cos\p{qa+\mu\phi} s_{\mu\mu}
  = \cos\p{qa} \f12 \sum_{L\,\t{even}}
  \obk{\tilde d_{\phi+}|D_{L,0}} D_{L,0}
  - \sin\p{qa} \f12 \sum_{L\,\t{odd}}
  \obk{\tilde d_{\phi-}|D_{L,0}} D_{L,0},
\end{align}
or, more compactly,
\begin{align}
  \sum_\mu \cos\p{qa+\mu\phi} s_{\mu\mu}
  = \sum_L w_L\p{qa} A_L^{(\phi)} D_{L,0},
  &&
  w_L\p{\theta} \equiv
  \begin{cases}
    \cos\theta & L~\t{even} \\
    \sin\theta & L~\t{odd}
  \end{cases},
  \label{eq:compact_SOC_drive}
\end{align}
with effective driving field amplitudes
\begin{align}
  A_L^{(\phi)}
  \equiv \p{-1}^L \f12 \obk{\tilde d_{\phi,\p{-1}^L}|D_{L,0}}
  = \p{-1}^L \sqrt{\f{2L+1}{n}}
  \sum_\mu \bk{I\mu;L,0|I\mu} w_L\p{\mu\phi}.
\end{align}
Substituting the result in \eqref{eq:compact_SOC_drive} into the
single-particle Hamiltonian in \eqref{eq:H_lat_spin} yields
\begin{align}
  H_{\t{lat}}^{(\phi)} = \sum_{q,L} B_L^{(\phi,q)} D_{L,0}^{(q)},
  &&
  B_L^{(\phi,q)} \equiv -J w_L\p{qa} A_L^{(\phi)}.
\end{align}

@@

The drive operators are defined by
\begin{align}
  D_{L,0} \equiv T_{L,0},
  &&
  D_{LM} \stackrel{M\ne0}{\equiv} \f{\sigma_M}{\sqrt{2}}
  \sp{T_{L\abs{M}} + \sign\p{M}T_{L\abs{M}}^\dag},
  &&
  \sigma_M \equiv \p{-1}^M \sign\p{M}^{3/2},
\end{align}
and can alternately be expressed as
\begin{align}
  D_{LM} = \f{\tau_M}{\sqrt{2}} \p{T_{LM} + \epsilon_M T_{L,-M}},
\end{align}
where
\begin{align}
  \tau_M \equiv
  \begin{cases}
    \sqrt{2} & M = 0, \\
    \p{-1}^M \sign\p{M}^{M+1/2} & M \ne 0
  \end{cases},
  &&
  \epsilon_M \equiv \p{-1}^M \sign\p{M},
\end{align}
which also implies that
\begin{align}
  T_{LM} = \f{\tilde\tau_M}{\sqrt{2}} \p{D_{LM} + i D_{L,-M}},
  &&
  \tilde\tau_M \equiv
  \begin{cases}
    \sqrt{2}/\p{1+i} & M = 0 \\
    \tau_M^* & M \ne 0
  \end{cases}.
\end{align}
In order to evaluate the product of two drive operators, we can thus
expand them in terms of transition operators, evaluate the
corresponding products of transition operators (see Appendix
\ref{sec:trans_prod}), and finally expand the result in terms of drive
operators.  The general product of two drive operators takes the form
\begin{align}
  D_{\ell_1 m_1} D_{\ell_2 m_2}
  = \f{\tau_{m_1}\tau_{m_2}}{\sqrt{2}}
  \sum_L \p{f_{\ell_1 m_1;\ell_2 m_2}^{L,m_1+m_2}
    E_{\ell_1 m_1;\ell_2 m_2}^{(L,+)}
    + f_{\ell_1 m_1;\ell_2,-m_2}^{L,m_1-m_2}
    E_{\ell_1 m_1;\ell_2 m_2}^{(L,-)}},
\end{align}
with operators
\begin{align}
  E_{\ell_1 m_1;\ell_2 m_2}^{(L,+)}
  &\equiv \sum_{s\in\set{\pm1}}
  \f12 \sp{\tilde\tau_{m_1+m_2}
    + i s \p{-1}^{L+\ell_1+\ell_2}
    \epsilon_{m_1} \epsilon_{m_2} \tilde\tau_{-\p{m_1+m_2}}}
  \sqrt{s} D_{L,s\p{m_1+m_2}},
  \\
  E_{\ell_1 m_1;\ell_2 m_2}^{(L,-)}
  &\equiv \sum_{s\in\set{\pm1}}
  \f12 \sp{\epsilon_{m_2} \tilde\tau_{m_1-m_2}
    + i s \p{-1}^{L+\ell_1+\ell_2}
    \epsilon_{m_1} \tilde\tau_{-\p{m_1-m_2}}}
  \sqrt{s} D_{L,s\p{m_1-m_2}}.
\end{align}
If $m_1\pm m_2=0$, these operators simplify to
\begin{align}
  E_{\ell_1 m;\ell_2,-m}^{(L,+)}
  &= \f1{\sqrt{2}} \sp{1 - \p{-1}^{L+\ell_1+\ell_2}
    \p{1-\delta_{m,0}}} D_{L,0}, \\
  E_{\ell_1 m;\ell_2 m}^{(L,-)}
  &= \f{\epsilon_m}{\sqrt{2}}
  \sp{1 + \p{-1}^{L+\ell_1+\ell_2}} D_{L,0},
\end{align}
and are otherwise
\begin{align}
  E_{\ell_1 m_1;\ell_2 m_2}^{(L,+)}
  &\stackrel{m_1+m_2\ne0}{=}
  \tau_{m_1+m_2}^* \sum_{s\in\set{\pm1}}
  \f12 \sp{1 + s \p{-1}^{L+\ell_1+\ell_2}
    \epsilon_{m_1} \epsilon_{m_2} \epsilon_{m_1+m_2}}
  \sqrt{s} D_{L,s\p{m_1+m_2}}, \\
  E_{\ell_1 m_1;\ell_2 m_2}^{(L,-)}
  &\stackrel{m_1-m_2\ne0}{=}
  \tau_{m_1-m_2}^* \sum_{s\in\set{\pm1}}
  \f12 \sp{\epsilon_{m_2} + s \p{-1}^{L+\ell_1+\ell_2}
    \epsilon_{m_1} \epsilon_{m_1-m_2}}
  \sqrt{s} D_{L,s\p{m_1-m_2}}.
\end{align}
If $\p{m_1,m_2}=\p{0,m}$, then we can use the fact that
$i\tau_m\tau_{-m}^*=\epsilon_m$ for $m\ne0$ to simplify
\begin{align}
  D_{\ell_1,0} D_{\ell_2 m}
  = \sum_L f_{\ell_1,0,\ell_2,m}^{Lm}
  \sum_{s\in\set{\pm1}} \f12 \sp{1 + s \p{-1}^{L+\ell_1+\ell_2}}
  \sqrt{s} D_{L,sm}.
\end{align}
